Regression Cube Analysis of Cohort Study Data

### 2015-06-21 draft.tex
references related work in the Cover Letter

>>>>

\magenta{
Maries et al.~\cite{GRACE} propose \texttt{GRACE}, a framework for visually exploring correlation of features with spatial and non-spatial geriatric data.
%%
Sparse Partial Least Squares Regression and Tikhonov Regularization are used to produce predictor subsets and quantify correlation strengths.
%%
A multi-view system linked spatial with non-spatial data and correlation coefficients are visualized using Kiviat diagrams (similar to star plots), correlations are plotted using p-values in the other views.
%%
Dendograms are used to select different brain regions. 
}
